Classifying Human Driving Behavior via Deep Neural Networks

### 2017-06-08 presentation/presentation.tex
updated presentation

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{frame}
\frametitle{Problem Statement}
This is problem statement
\end{frame}

\begin{frame}
\frametitle{Project Background}
This is project background
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Background}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Introduction}
\begin{itemize}
\item The concept of artificial neurons was introduced by Warren McCullock and Walter Pitts
\item Neural network consists of many artificial neurons
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Introduction}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{../paper/pictures/figures/detail_NN.png}
    \caption{Example of a Neural Network}
    \label{fig:detail_NN}
\end{figure}

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.3\textwidth]{../paper/pictures/figures/NN.png}
    \caption{Simplified Neural Network}
    \label{fig:NN}
\end{figure}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Error Function:
$$J(\bold{V}, \bold{W}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2 =\frac{1}{2}\sum_{i}(y_i-g(\bold{h}(\vec{X}\bold{V})\bold{W_i}))^2$$

Update $W_{ij}$ - $i$th neuron for $j$th input:
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/BP1.png}
    \caption{Back-propagation for $W_{ij}$}
    \label{fig:BP1}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Update $W_{ij}$ - $i$th neuron for $j$th input:
$$
{{W_{ij}}^{next}}
= W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}
= W_{ij} - \eta\frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
= W_{ij} + \eta(y_i-o_i)o_i(1-o_i)H_j
$$

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.25\textwidth]{../paper/pictures/figures/train_MAE1.png}
    \caption{Pretraining First Step}
    \label{fig:train_MAE1}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/pictures/figures/train_MAE2.png}
    \caption{Pretraining Second Step}
    \label{fig:train_MAE2}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/train_MAE3.png}
    \caption{Pretraining Thrid Step}
    \label{fig:train_MAE3}
\end{figure}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Environment}
Tux
\begin{itemize}
\item Processors:
\item Memory:
\item Tensorflow 0.12.1
\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.25\textwidth]{../paper/pictures/figures/train_new_MAE1.png}
    \caption{First Step of New Way to train MAE}
    \label{fig:train_NMAE1}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/pictures/figures/train_new_MAE2.png}
    \caption{Second Step of New Way to train MAE}
    \label{fig:train_NMAE2}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/train_new_MAE3.png}
    \caption{Thrid Step of New Way to train MAE}
    \label{fig:train_NMAE3}
\end{figure}
\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{frame}
\frametitle{Problem Statement}
\begin{itemize}
\item Modern car systems collect real-time data of the car status and driving behavior of the driver
\item Those data is worth for healthcare and research
\item Using driving behavior data to diagnose medical conditions
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Project Background}
\begin{itemize}
\item Classify driving simulation data from novice and expert drivers using several different neural network models
\item Explain LSTM and Auto-encoder
\item Compare result from three different neural network models
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Background}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Introduction}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{../paper/pictures/figures/general_AN.png}
    \caption{General Artificial Neuron}
    \label{fig:general_AN}
\end{figure}

\begin{itemize}
\item An artificial neuron has input signals, weights, bias, and activation function
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Introduction}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/figures/detail_NN.png}
    \caption{Example of a Neural Network}
    \label{fig:detail_NN}
\end{figure}

\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/NN.png}
    \caption{Simplified Neural Network}
    \label{fig:NN}
\end{figure}
\end{columns}

\begin{itemize}
\item Neural network is a network made up many artificial neurons
\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.45\textwidth]{../paper/pictures/figures/MLP.png}
    \caption{One Hidden Layer MLP}
    \label{fig:MLP}
\end{figure}

Activation Function:
$$f(z)=g(z)=sigm(z)=\frac{1}{1+e^{-z}}$$

Error Function:
$$J(\bold{V}, \bold{W}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2 =\frac{1}{2}\sum_{i}(y_i-g(\bold{h}(\vec{X}\bold{V})\bold{W_i}))^2$$

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.25\textwidth]{../paper/pictures/figures/train_MAE1.png}
    \caption{Pretraining First Step}
    \label{fig:train_MAE1}
\end{figure}

$$E(input, data\_from\_first\_decoder)$$
$$=E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/pictures/figures/train_MAE2.png}
    \caption{Pretraining Second Step}
    \label{fig:train_MAE2}
\end{figure}

$$E(data\_from\_first\_encoder, data\_from\_second\_decoder)$$
$$=E(\bold{f_1}(\vec{X}\bold{E_1^{fixed}}), \bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2})\bold{D_2}))$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/train_MAE3.png}
    \caption{Pretraining Thrid Step}
    \label{fig:train_MAE3}
\end{figure}

$$E(data\_from\_second\_encoder, data\_from\_third\_decoder)$$
$$=E(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}}), \bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}})\bold{E_3})\bold{D_3}))$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/example_MAE.png}
    \caption{Multilayer Auto-encoder Example}
    \label{fig:example_MAE}
\end{figure}

$$E(input, output)$$
$$=E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
%\begin{frame}
%\frametitle{Environment}
%Tux
%\begin{itemize}
%\item Processors:
%\item Memory:
%\item Tensorflow 0.12.1
%\end{itemize}
%\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.25\textwidth]{../paper/pictures/figures/train_new_MAE1.png}
    \caption{First Step of New Way to train MAE}
    \label{fig:train_NMAE1}
\end{figure}

$$E(input, output)$$
$$=E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/pictures/figures/train_new_MAE2.png}
    \caption{Second Step of New Way to train MAE}
    \label{fig:train_NMAE2}
\end{figure}

$$E(input, output)$$
$$=E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{D_2})\bold{D_1}))$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/train_new_MAE3.png}
    \caption{Thrid Step of New Way to train MAE}
    \label{fig:train_NMAE3}
\end{figure}

$$E(input, output)$$
$$=E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
\end{frame}
